Biotic invasions fuck with the manageability of pollination networks

### 2017-02-14 paper/supp_info_2.Rmd
Minor changes to network properties table

```{r calc-network-properties, echo = F, message = F}
net_prop <- net %>%
	plyr::ldply(function(x){
		x <- keep_largest_component(x)
		bipartite::networklevel(igraph::as_incidence_matrix(x, 
																												types = igraph::V(x)$type == "pla",
																												attr = "weight"),
														index = c("connectance", "web asymmetry", 
																			"ISA", 
																			"weighted NODF")) %>%
			as.list() %>% as.data.frame() %>%
			dplyr::mutate(n_sp = length(igraph::V(x)),
										n_pla = sum(igraph::V(x)$type == "pla"),
										n_pol = sum(igraph::V(x)$type == "pol"))
	})

>>>>

```{r calc-network-properties, echo = F, message = F}
net_prop <- net %>%
	plyr::ldply(function(x){
		x <- keep_largest_component(x)
		n_pla <- sum(igraph::V(x)$type == "pla")
		n_pol <- sum(igraph::V(x)$type == "pol")
		bipartite::networklevel(igraph::as_incidence_matrix(x, 
																												types = igraph::V(x)$type == "pla",
																												attr = "weight"),
														index = c("connectance", "web asymmetry", 
																			"ISA", 
																			"weighted NODF")) %>%
			as.list() %>% as.data.frame() %>%
			dplyr::mutate(n_sp = length(igraph::V(x))) %>%
			dplyr::mutate(n_pla = n_pla,
										n_pol = n_pol)
	})
